parameters

### 2020-02-12 manuscript/drafts/manuscript.Rmd
meeting notes
add doc2vec, random forest

Numerical representation of texts
To perform a learning algorithm on the abstract, the content of the abstracts needs to be represented numerical.
To perform learning algorithms on the abstracts, their content has to be represented in a numerical way. 
This is done by transforming the textual content of the abstracts into numerical feature vectors. 
A classical example representation of texts is by 'bag of words' features, where for each text the number of occurrences of each word is stored. This leads to n features, where n is the number of distinct words in the texts. [@scikit-learn]

@@

* Doc2Vec [@Le2014]
* Tfidf 
* SBERT
* embeddingIdf

The model is typically a learning algorithm used to predict the relevance of text.
The following models will be compared:

* Naive Bayes 
* Random Forests
* Support Vector Machine 
* Logistic Regression 
* **Dense Neural Network**

@@

```{r}
kable(tab, "latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```

@@

### Random Forests

@@

### *Dense Neural Network*

@@

## Feature Extraction Strategies

## amount of training data
n_instances = number of papers queried each query
n_queries = number of queries
n_prior_included: 5
n_prior_excluded:

>>>>

Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

A classical example of word embeddings is 'bag of words'. For each each text, the number of occurrences of each word is stored. This leads to n features, where n is the number of distinct words in the texts. [@scikit-learn]

Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.

corpus = all the text:

@@

The model is typically a learning algorithm used to predict the relevance of text.

@@

```{r}
kable(tab, "latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```
### Feature Extraction Strategies 
split_ta = overall hyperparameter

#### TF-IDF
The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".

Term-frequency Inverse Document Frequency [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.

##### hyperparameters 
    ngram_max: int
            Can use up to ngrams up to ngram_max. For example in the case of
            ngram_max=2, monograms and bigrams could be used.

#### Doc2Vec
Predicts words from context. 
Aims at capturing the relations between word (man-woman, king-queen).
[@Le2014]. Using a neural network.

using Continuous Bag-of-Words (CBOW), Skip-Gram model, ....
Word vector _W_ and extra: document vector _D_, trained to predict words in the text.

From gensim [@Rehurek2010].

        Arguments
        ---------
        vector_size: int
            Output size of the vector.
        epochs: int
            Number of epochs to train the doc2vec model.
        min_count: int
            Minimum number of occurences for a word in the corpus for it to
            be included in the model.
        workers: int
            Number of threads to train the model with.
        window: int
            Maximum distance over which word vectors influence each other.
        dm_concat: int
            Whether to concatenate word vectors or not.
            See paper for more detail.
        dm: int
            Model to use.
            0: Use distribute bag of words (DBOW).
            1: Use distributed memory (DM).
            2: Use both of the above with half the vector size and concatenate
            them.
        dbow_words: int
            Whether to train the word vectors using the skipgram metho

#### SBERT

BERT-base model with mean-tokens pooling [@Reimers2019]

#### embeddingIdf 
This model averages the weighted word vectors of all the words in the text,
in order to get a single feature vector for each text. The weights are provided by the inverse document frequencies

@@

### Random Forests
A number of decision trees are fit on bootstrapped samples of the original data, 
[@Breiman2001]
RandomForestClassifier from sklearn

Arguments
        ---------
        n_estimators: int
            Number of estimators.
        max_features: int
            Number of features in the model.
        class_weight: float
            Class weight of the inclusions.
        random_state: int, RandomState
            Set the random state of the RNG.
        """

@@

### __Dense Neural Network__

@@

## amount of training data

* n_instances = number of papers queried each query
* n_queries = number of queries
* n_prior_included: 5
* n_prior_excluded:
